---
title: "Onset and duration analysis of sentence production fMRI experiment"
author: "Laura Giglio"
date: "2019 09 24"
output:
  word_document: default
  pdf_document: default
  html_document: default
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#knitr::opts_knit$set(root.dir = '/project/3011226.01/behavioural/')
knitr::opts_knit$set(root.dir ='P:/3011226.01/behavioural/')
packages <- c("ggplot2", "tidyverse", "reshape2", "lme4", "car")
if (length(setdiff(packages, rownames(installed.packages()))) > 0) {
  install.packages(setdiff(packages, rownames(installed.packages())))  
}

rm(list=ls())


library(ggplot2)
#library(plyr)
#library(dplyr)
library(tidyverse)
#library(plotrix)
library(reshape2)
#library(cowplot)
#library(readr)
library(lme4)
#library(stringi)
library(car)
library(mpinltheme)

#source("/home/language/laugig/R/RainCloudPlots-master/RainCloudPlots-master/tutorial_R/R_rainclouds.R")
source("M:/R/RainCloudPlots-master/RainCloudPlots-master/tutorial_R/R_rainclouds.R")

```
Importing coding data and Importing onset and offset marking

```{r import, echo=FALSE, warning=FALSE}

#import coding results
#setwd("project/3011226.01/behavioural/")
coded_subjs = c("01","02","04","07","08","09","10","11","12","14","15","16","17","18","19","20","21","22","24","25", "26","27","28", "29","30","31","32","33","34","35","36","37","38","39","40","41","42","43","44","46")
accdata = data.frame()
praatdata = data.frame()
for (isubj in coded_subjs) {
  
  #open file
  #dirpath = paste("/project/3011226.01/behavioural/s", isubj, sep="")
  dirpath = paste("P:/3011226.01/behavioural/s", isubj, sep="")

  allfilenames = dir(dirpath, pattern = "P._run*")
  for (irun in 1:length(allfilenames)) {
    
    # get run order
    #run_order = read.table(paste("/project/3011226.01/behavioural/s", isubj, "/s", isubj, ".txt", sep="" ), header = T, sep = '\t')
    run_order = read.table(paste("P:/3011226.01/behavioural/s", isubj, "/s", isubj, ".txt", sep="" ), header = T, sep = '\t')

    # get accuracy files
    #filename = paste("/project/3011226.01/behavioural/s", isubj, "/", allfilenames[run_order$Order_runs[irun]], sep="")
    filename = paste("P:/3011226.01/behavioural/s", isubj, "/", allfilenames[run_order$Order_runs[irun]], sep="")

    temp = read.delim(filename, header = T, sep = '\t')
    temp$Actor <- NULL
    temp$X <- NULL
    # add subj and run numer
    #subjnr = unlist(strsplit(filename, "_"))[2]
    temp$participant = as.factor(isubj)
    temp$run = as.factor(irun)
  
    #combine with other files
    accdata = rbind(accdata,temp)

    # get onset offset times from praat txt file
    #filename2 = paste("/project/3011226.01/behavioural/s", isubj, "/", irun, "/filtered/onsets_durationAutomatic.txt", sep="")
    filename2 = paste("P:/3011226.01/behavioural/s", isubj, "/", irun, "/filtered/onsets_durationAutomatic.txt", sep="")

    temp2 = read.table(filename2, header = F, sep = '\t')
    
    # add subj and run number
    temp2$participant = as.factor(isubj)
    
    temp2$run = as.factor(irun)
    #combine with other files
    praatdata = rbind(praatdata,temp2)
  }
}

write.csv(praatdata,"P:/3011226.01/behavioural/praat_data.csv",row.names=FALSE)
write.csv(accdata,"P:/3011226.01/behavioural/accuracy_data.csv",row.names=FALSE)


```

Merging accuracy and praat data

```{r mergedata, echo=FALSE}
# first need to sort praat data in "normal" order
praatdata$V2 <- as.character(praatdata$V2)
for (n in 1:nrow(praatdata)) {
  praatdata$trialnr[n] = unlist(strsplit(praatdata$V2[n], "_"))[3]
}
praatdata = subset(praatdata, select= -V5)
praatdata = subset(praatdata, select= -V1)
colnames(praatdata)[1] = 'Recording'
colnames(praatdata)[2] = 'Onset'
colnames(praatdata)[3] = 'Offset'

praatdata <- praatdata[order(as.integer(praatdata$participant), as.integer(praatdata$run), as.integer(praatdata$trialnr)),]

alldata = cbind(praatdata,accdata)
alldata = subset(alldata, select= -participant)
alldata = subset(alldata, select= -run.1)
 
```
## Accuracy

Legend:

FIL = fillers, "De man raakt de vrouw" (the man touches the woman)

NP = noun phrase, "denken, springen, de man, de vrouw" (to think, to jump, the man, the woman)

SC = coordinated sentence, "de man rent, de vrouw springt" (the man runs, the woman jumps)

SE = embedded sencence, "de man denkt dat de vrouw springt" (the man thinks that the woman jumps)



Accuracy analysis

```{r stats accuracy, echo=FALSE}

alldata$Accuracy2 = ifelse(alldata$Accuracy2 == 1, 1,2)

alldata2 = droplevels(alldata[alldata$Condition != "FIL",])
alldata2$Accuracy2 = ifelse(alldata2$Accuracy2 == 1, 1,0)
alldata2$Trial = as.factor(alldata2$Trial)
table(alldata2$Accuracy2,alldata2$participant)


modelAcc = glmer(Accuracy2 ~ Condition + (1|participant)+ (1|Verb1) + (1|Verb2) , data=alldata2, family='binomial',control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e6)))
# doesn't converge with condition|participant
summary(modelAcc)
Anova(modelAcc) # to get effect of Condition

#to get all pairwise comparisons
alldata2$Condition <- relevel(alldata2$Condition, ref = "NP")
modelAcc2 = glmer(Accuracy2 ~ Condition + (1|participant) + (1|Verb1) + (1|Verb2), data=alldata2, family='binomial')
summary(modelAcc2)

``` 

```{r error type analysis, echo=FALSE}
alldata$ErrorType2=0
alldata$ErrorType1=0
alldata$ErrorType = as.character(alldata$ErrorType)
alldata$ErrorType[is.na(alldata$ErrorType)]=0
for (n in 1:length(alldata$ErrorType)) {
  if (alldata$Accuracy2[n] == 2) {
    if (nchar(alldata$ErrorType[n])>2) {
      alldata$ErrorType2[n]=str_sub(alldata$ErrorType[n],-1)
      alldata$ErrorType1[n]=str_sub(alldata$ErrorType[n],1,1)
    }
    else if (nchar(alldata$ErrorType[n])>1) {
      alldata$ErrorType1[n]=str_sub(alldata$ErrorType[n],1,1)
    }
    else {
      alldata$ErrorType1[n]=alldata$ErrorType[n]
    }
  }
} 
a=table(alldata$ErrorType1)
b=table(alldata$ErrorType2)
```

```{r correct plots, echo=FALSE}

#average of correct trials per condition
accuracy <- data.frame
accuracy <- alldata %>% group_by(Condition,participant) %>% summarise(correct = sum(Accuracy2==1))

accuracy$correct = accuracy$correct/80*100 #to get percentage

mean_accuracy <- accuracy %>% group_by(Condition) %>% summarise(meanC = mean(correct))
mean_participant <- accuracy %>% group_by(participant) %>% summarise(meanC = mean(correct))
#mean_participant2 <- alldata %>% group_by(participant) %>% summarise(correct = sum(Accuracy2==1)/320*100)

m = mean(mean_participant$meanC)
sdp = sd(mean_participant$meanC)
# mean accuracy per participant
ggplot(mean_participant, aes(x=participant, y=meanC, fill = meanC)) + geom_bar(stat='identity')

accuracyplot = ggplot(accuracy, aes(x=Condition, y = correct)) +
  geom_jitter(width=.1,aes(color=participant)) + labs(y= '% Correct responses' ) +
  geom_violin(alpha=0.3)
accuracyplot

```

```{r accuracyplot, echo=FALSE}

#change condition names in line with paper
accuracy$structure <- ifelse(accuracy$Condition == "NP","C1",ifelse(accuracy$Condition == "SC","C2",(ifelse(accuracy$Condition == "SE","C4","FIL"))))
# recalculate means to get new condition names
mean_accuracy <- accuracy %>% group_by(structure) %>% summarise(meanC = mean(correct),sdC=sd(correct),sem=sd(correct)/sqrt(40))

pAcc <- ggplot(accuracy,aes(x=structure,y=correct, fill = structure, colour = structure))+
  geom_flat_violin(position = position_nudge(x = .25, y = 0),adjust =2)+
  geom_point(position = position_jitter(width = .15), size = .25)+
  geom_point(data = mean_accuracy, aes(x = structure, y = meanC), position = position_nudge(.25), size = 0.3,colour = "BLACK")+
  geom_errorbar(data = mean_accuracy, aes(x = structure, y = meanC, ymin = meanC-sem, ymax = meanC+sem), position = position_nudge(.25), colour = "BLACK", width = 0.1, size = 0.4)+
  ylab('Percentage correct')+xlab('Condition')+theme_mpinl_general()+guides(fill = FALSE, colour = FALSE) +
  ggtitle("Accuracy")
pAcc + scale_colour_discrete_mpinl()+  scale_fill_discrete_mpinl()
ggsave('P:/3011226.01/figures/accuracy_plot_colour.png', width = 4, height = 3)

pAcc + scale_colour_grey()+  scale_fill_grey()
ggsave(
  'P:/3011226.01/figures/accuracy_plot_grey.tif',
  plot = last_plot(),
  device = "tiff",
  path = NULL,
  scale = 1,
  width = 80,
  height = 60,
  units = "mm",
  dpi = 900,
  limitsize = TRUE
)

```

```{r makecorrect, echo=FALSE}
#only keep correct trials
correctdata = droplevels(alldata[alldata$Accuracy2=='1',])
correctdata$Duration = correctdata$Offset - correctdata$Onset
#correctdata = read.csv('correctdata.csv')
#correctdata = write.csv(correctdata, 'correctdata.csv', row.names = FALSE)
table(correctdata$participant,correctdata$Condition)

```

```{r onset time analysis, echo=TRUE}
correctdata2 = droplevels(correctdata[correctdata$Condition != "FIL",]) # drop filler condition
table(correctdata2$participant,correctdata2$Condition)
#write.csv(correctdata2,"P:/3011226.01/bids/derivatives/SPM/ROI/onsets.csv",row.names=FALSE)

correctdata2$logOnset = log(correctdata2$Onset)

modelOn = lmer(logOnset ~ Condition + (Condition|participant) + (1|Verb1)+(1|Verb2), correctdata2, REML=FALSE,control=lmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))) 
summary(modelOn)
Anova(modelOn)
anova(modelOn)

#relevel to get difference between SC and SE
correctdata2$Condition <- relevel(correctdata2$Condition, ref = "SC")
modelOn2 = lmer(logOnset ~ Condition + (Condition| participant) + (1|Verb1)+(1|Verb2), correctdata2, REML=FALSE,control=lmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))) 
summary(modelOn2)

Anova(modelOn2)
anova(modelOn2)

# ts <- fixef(modelOn2) / sqrt(diag(vcov(modelOn2)))
# print(round(ts,2))
# ps <- 2*(1-pnorm(abs(ts)))
# print(round(ps,3))

```

```{r duration time analysis, echo=TRUE}
correctdata2$logDuration = log(correctdata2$Duration)


modelD = lmer(logDuration ~ Condition + (Condition| participant) + (1|Verb1)+ (1|Verb2), correctdata2, REML=FALSE,control=lmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))) 
summary(modelD)
Anova(modelD)

#relevel to get difference between SC and SE
correctdata2$Condition <- relevel(correctdata2$Condition, ref = "SC")
modelD2 = lmer(logDuration ~ Condition + (Condition| participant) + (1|Verb1)+ (1|Verb2), correctdata2, REML=FALSE,control=lmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))) 
summary(modelD2)


```

## Onsets and duration means for each participant

```{r onsetmeans, echo=FALSE}

#average of correct trials per condition
onsets <- data.frame
onsets <- correctdata %>% group_by(Condition,participant) %>% summarise(onset = mean(Onset))
durations <- data.frame
durations <- correctdata %>% group_by(Condition,participant) %>% summarise(duration = mean(Offset-Onset))



onsets$structure <- ifelse(onsets$Condition == "NP","C1",ifelse(onsets$Condition == "SC","C2",(ifelse(onsets$Condition == "SE","C4","FIL"))))
durations$structure <- ifelse(durations$Condition == "NP","C1",ifelse(durations$Condition == "SC","C2",(ifelse(durations$Condition == "SE","C4","FIL"))))

mean_times = correctdata %>% group_by(Condition) %>% summarise(meanOnset = mean(Onset),sdO=sd(Onset),semO=sd(Onset)/sqrt(40),meanDuration = mean(Offset-Onset),sdD=sd(Offset-Onset),semD=sd(Offset-Onset)/sqrt(40))

mean_times$structure <- ifelse(mean_times$Condition == "NP","C1",ifelse(mean_times$Condition == "SC","C2",(ifelse(mean_times$Condition == "SE","C4","FIL"))))


```
```{r raincloud plot onset condition with means, echo=FALSE}
pOnset <- ggplot(onsets,aes(x=structure,y=onset, fill = structure, colour = structure))+
  geom_flat_violin(position = position_nudge(x = .25, y = 0),adjust =2)+
  geom_point(position = position_jitter(width = .15), size = .25)+
  geom_point(data = mean_times, aes(x = structure, y = meanOnset), position = position_nudge(.25), size=1, colour = "BLACK")+
  geom_errorbar(data = mean_times, aes(x = structure, y = meanOnset, ymin = meanOnset-semO, ymax = meanOnset+semO), position = position_nudge(.25), colour = "BLACK", width = 0.1, size = 0.6)+
  ylab('Onset (sec)')+xlab('Condition')+theme_mpinl_general()+guides(fill = FALSE, colour = FALSE) +
  scale_colour_grey()+  scale_fill_grey() +
  ggtitle("Production Onset")

pOnset 

pOnset +  scale_colour_discrete_mpinl()+  scale_fill_discrete_mpinl()

```

```{r raincloud plot duration condition with means, echo=FALSE}
pDuration <- ggplot(durations,aes(x=structure,y=duration, fill = structure, colour = structure))+
  geom_flat_violin(position = position_nudge(x = .25, y = 0),adjust =2)+
  geom_point(position = position_jitter(width = .15), size = .25)+
  geom_point(data = mean_times, aes(x = structure, y = meanDuration), position = position_nudge(.25),size=1, colour = "BLACK")+
  geom_errorbar(data = mean_times, aes(x = structure, y = meanDuration, ymin = meanDuration-semD, ymax = meanDuration+semD), position = position_nudge(.25), colour = "BLACK", width = 0.1, size = 0.6)+
  ylab('Duration (sec)')+xlab('Condition')+theme_mpinl_general()+guides(fill = FALSE, colour = FALSE) +
  #scale_colour_discrete_mpinl()+  scale_fill_discrete_mpinl()+
  scale_color_grey() + scale_fill_grey() +
  ggtitle("Production Duration")
pDuration

```

```{r combine plots, echo=FALSE}
all_plot <- plot_grid(pOnset, pDuration, labels="AUTO")
all_plot
#ggsave('P:/3011226.01/figures/onset_duration.png', width = 6, height = 3)

ggsave(
  'P:/3011226.01/figures/onset_duration.tif',
  plot = last_plot(),
  device = "tiff",
  path = NULL,
  scale = 1,
  width = 180,
  height = 70,
  units = "mm",
  dpi = 900,
  limitsize = TRUE
)

```



