---
title: "Onset and duration analysis of sentence production fMRI experiment"
author: "Laura Giglio"
date: "2019 09 24"
output:
  word_document: default
  pdf_document: default
  html_document: default
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#knitr::opts_knit$set(root.dir = '/project/3011226.01/behavioural/')
knitr::opts_knit$set(root.dir ='P:/3011226.01/behavioural/')

library(ggplot2)
library(plyr)
library(dplyr)
library(tidyverse)
library(plotrix)
library(reshape2)
rm(list=ls())
#setwd("P:/3011226.01/behavioural/")
packages <- c("ggplot2", "dplyr", "lavaan", "plyr", "cowplot", "rmarkdown", 
              "readr", "caTools", "bitops")
if (length(setdiff(packages, rownames(installed.packages()))) > 0) {
  install.packages(setdiff(packages, rownames(installed.packages())))  
}
library(cowplot)
library(dplyr)
library(readr)
library(lme4)
library(stringi)
library(car)
library(mpinltheme)
#source("/home/language/laugig/R/RainCloudPlots-master/RainCloudPlots-master/tutorial_R/R_rainclouds.R")
source("M:/R/RainCloudPlots-master/RainCloudPlots-master/tutorial_R/R_rainclouds.R")

#source("summarySE.R")
#source("simulateData.R")
```
Importing coding data and Importing onset and offset marking

```{r import, echo=FALSE, warning=FALSE}

#import coding results
#setwd("project/3011226.01/behavioural/")
coded_subjs = c("01","02","04","07","08","09","10","11","12","14","15","16","17","18","19","20","21","22","24","25", "26","27","28", "29","30","31","32","33","34","35","36","37","38","39","40","41","42","43","44","46")
accdata = data.frame()
praatdata = data.frame()
for (isubj in coded_subjs) {
  
  #open file
  #dirpath = paste("/project/3011226.01/behavioural/s", isubj, sep="")
  dirpath = paste("P:/3011226.01/behavioural/s", isubj, sep="")

  allfilenames = dir(dirpath, pattern = "P._run*")
  for (irun in 1:length(allfilenames)) {
    
    # get run order
    #run_order = read.table(paste("/project/3011226.01/behavioural/s", isubj, "/s", isubj, ".txt", sep="" ), header = T, sep = '\t')
    run_order = read.table(paste("P:/3011226.01/behavioural/s", isubj, "/s", isubj, ".txt", sep="" ), header = T, sep = '\t')

    # get accuracy files
    #filename = paste("/project/3011226.01/behavioural/s", isubj, "/", allfilenames[run_order$Order_runs[irun]], sep="")
    filename = paste("P:/3011226.01/behavioural/s", isubj, "/", allfilenames[run_order$Order_runs[irun]], sep="")

    temp = read.delim(filename, header = T, sep = '\t')
    temp$Actor <- NULL
    temp$X <- NULL
    # add subj and run numer
    #subjnr = unlist(strsplit(filename, "_"))[2]
    temp$participant = as.factor(isubj)
    temp$run = as.factor(irun)
  
    #combine with other files
    accdata = rbind(accdata,temp)

    # get onset offset times from praat txt file
    #filename2 = paste("/project/3011226.01/behavioural/s", isubj, "/", irun, "/filtered/onsets_durationAutomatic.txt", sep="")
    filename2 = paste("P:/3011226.01/behavioural/s", isubj, "/", irun, "/filtered/onsets_durationAutomatic.txt", sep="")

    temp2 = read.table(filename2, header = F, sep = '\t')
    
    # add subj and run number
    temp2$participant = as.factor(isubj)
    
    temp2$run = as.factor(irun)
    #combine with other files
    praatdata = rbind(praatdata,temp2)
  }
}

write.csv(praatdata,"P:/3011226.01/behavioural/praat_data.csv",row.names=FALSE)
write.csv(accdata,"P:/3011226.01/behavioural/accuracy_data.csv",row.names=FALSE)


```

Merging accuracy and praat data

```{r mergedata, echo=FALSE}
# first need to sort praat data in "normal" order
praatdata$V2 <- as.character(praatdata$V2)
for (n in 1:nrow(praatdata)) {
  praatdata$trialnr[n] = unlist(strsplit(praatdata$V2[n], "_"))[3]
}
praatdata = subset(praatdata, select= -V5)
praatdata = subset(praatdata, select= -V1)
colnames(praatdata)[1] = 'Recording'
colnames(praatdata)[2] = 'Onset'
colnames(praatdata)[3] = 'Offset'

praatdata <- praatdata[order(as.integer(praatdata$participant), as.integer(praatdata$run), as.integer(praatdata$trialnr)),]

alldata = cbind(praatdata,accdata)
alldata = subset(alldata, select= -participant)
alldata = subset(alldata, select= -run.1)
 
```
## Accuracy

Legend:

FIL = fillers, "De man raakt de vrouw" (the man touches the woman)

NP = noun phrase, "denken, springen, de man, de vrouw" (to think, to jump, the man, the woman)

SC = coordinated sentence, "de man rent, de vrouw springt" (the man runs, the woman jumps)

SE = embedded sencence, "de man denkt dat de vrouw springt" (the man thinks that the woman jumps)



Correct number of trials per participant

```{r stats correct, echo=FALSE}
#alldata$Coding[875] = 1
alldata$Accuracy2 = ifelse(alldata$Accuracy2 == 1, 1,2)


alldata2 = droplevels(alldata[alldata$Condition != "FIL",])
alldata2$Accuracy2 = ifelse(alldata2$Accuracy2 == 1, 1,0)
alldata2$Trial = as.factor(alldata2$Trial)
table(alldata2$Accuracy2,alldata2$participant)

#control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e6))

#contrasts(alldata2$Condition) <- contr.Sum(levels(alldata2$Condition)) for deviation coding
modelAcc = glmer(Accuracy2 ~ Condition + (1|participant)+ (1|Verb1) + (1|Verb2) , data=alldata2, family='binomial',control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e6)))
# doesn't converge with condition|participant, even though variance was quite high...
summary(modelAcc)
Anova(modelAcc) # to get effect of Condition

#to get all pairwise comparisons
alldata2$Condition <- relevel(alldata2$Condition, ref = "NP")
modelAcc2 = glmer(Accuracy2 ~ Condition + (1|participant) + (1|Verb1) + (1|Verb2), data=alldata2, family='binomial')
summary(modelAcc2)

``` 

```{r error type analysis, echo=FALSE}
alldata$ErrorType2=0
alldata$ErrorType1=0
alldata$ErrorType = as.character(alldata$ErrorType)
alldata$ErrorType[is.na(alldata$ErrorType)]=0
for (n in 1:length(alldata$ErrorType)) {
  if (alldata$Accuracy2[n] == 2) {
    if (nchar(alldata$ErrorType[n])>2) {
      alldata$ErrorType2[n]=str_sub(alldata$ErrorType[n],-1)
      alldata$ErrorType1[n]=str_sub(alldata$ErrorType[n],1,1)
    }
    else if (nchar(alldata$ErrorType[n])>1) {
      alldata$ErrorType1[n]=str_sub(alldata$ErrorType[n],1,1)
    }
    else {
      alldata$ErrorType1[n]=alldata$ErrorType[n]
    }
  }
} 
a=table(alldata$ErrorType1)
b=table(alldata$ErrorType2)
```

```{r correct plots, echo=FALSE}

#average of correct trials per condition
accuracy <- data.frame
accuracy <- alldata %>% group_by(Condition,participant) %>% summarise(correct = sum(Accuracy2==1))

accuracy$correct = accuracy$correct/80*100 #to get percentage

mean_accuracy <- accuracy %>% group_by(Condition) %>% summarise(meanC = mean(correct))
mean_participant <- accuracy %>% group_by(participant) %>% summarise(meanC = mean(correct))
#mean_participant2 <- alldata %>% group_by(participant) %>% summarise(correct = sum(Accuracy2==1)/320*100)

m = mean(mean_participant$meanC)
sdp = sd(mean_participant$meanC)
# mean accuracy per participant
ggplot(mean_participant, aes(x=participant, y=meanC, fill = meanC)) + geom_bar(stat='identity')

#mean accuracy per condition
ggplot(accuracy, aes(x=Condition, y=correct)) + geom_bar(stat='identity')

#ggplot(accuracy, aes(x=correct)) + geom_bar()

```

```{r accuracyplot, echo=FALSE}
accuracyplot = ggplot(accuracy, aes(x=Condition, y = correct)) +
  geom_jitter(width=.1,aes(color=participant)) + labs(y= '% Correct responses' ) +
  geom_violin(alpha=0.3)
#ggsave('accuracy_plot.pdf', plot=accuracyplot)
accuracyplot

accuracy$structure <- ifelse(accuracy$Condition == "NP","C1",ifelse(accuracy$Condition == "SC","C2",(ifelse(accuracy$Condition == "SE","C4","FIL"))))

mean_accuracy <- accuracy %>% group_by(structure) %>% summarise(meanC = mean(correct),sdC=sd(correct),sem=sd(correct)/sqrt(40))
mean_accuracy

p1 <- ggplot(accuracy,aes(x=structure,y=correct, fill = structure, colour = structure))+
  geom_flat_violin(position = position_nudge(x = .25, y = 0),adjust =2)+
  geom_point(position = position_jitter(width = .15), size = .25)+
  geom_point(data = mean_accuracy, aes(x = structure, y = meanC), position = position_nudge(.25), colour = "BLACK")+
  geom_errorbar(data = mean_accuracy, aes(x = structure, y = meanC, ymin = meanC-sem, ymax = meanC+sem), position = position_nudge(.25), colour = "BLACK", width = 0.1, size = 0.8)+
  ylab('Percentage correct')+xlab('Condition')+theme_mpinl_general()+guides(fill = FALSE, colour = FALSE) +
  scale_colour_discrete_mpinl()+
  scale_fill_discrete_mpinl()+
  ggtitle("Accuracy")
p1
ggsave('P:/3011226.01/figures/accuracy_plot.png', width = 4, height = 3)
ggsave(
  'P:/3011226.01/figures/accuracy_plot.tif',
  plot = last_plot(),
  device = "tiff",
  path = NULL,
  scale = 1,
  width = 80,
  height = 80,
  units = "mm",
  dpi = 300,
  limitsize = TRUE
)

p2 <- ggplot(accuracy,aes(x=structure,y=correct, fill = structure, colour = structure))+
  geom_flat_violin(position = position_nudge(x = .25, y = 0),adjust =2)+
  geom_point(position = position_jitter(width = .15), size = .8)+
  geom_point(data = mean_accuracy, aes(x = structure, y = meanC), position = position_nudge(.25), colour = "BLACK")+
  geom_errorbar(data = mean_accuracy, aes(x = structure, y = meanC, ymin = meanC-sem, ymax = meanC+sem), position = position_nudge(.25), colour = "BLACK", width = 0.1, size = 0.8)+
  ylab('Percentage correct')+xlab('Condition')+theme_mpinl_poster()+guides(fill = FALSE, colour = FALSE) +
  scale_colour_discrete_mpinl()+
  scale_fill_discrete_mpinl()+
  ggtitle("Accuracy")
p2

ggsave('P:/3011226.01/figures/accuracy_poster.png', width = 8, height = 7)
```

```{r makecorrect, echo=FALSE}
#only keep correct trials
correctdata = droplevels(alldata[alldata$Accuracy2=='1',])
correctdata$Duration = correctdata$Offset - correctdata$Onset
#correctdata = read.csv('correctdata.csv')
#correctdata = write.csv(correctdata, 'correctdata.csv', row.names = FALSE)
table(correctdata$participant,correctdata$Condition)

```

```{r onset time analysis, echo=TRUE}
correctdata2 = droplevels(correctdata[correctdata$Condition != "FIL",]) # drop filler condition
table(correctdata2$participant,correctdata2$Condition)
write.csv(correctdata2,"P:/3011226.01/bids/derivatives/SPM/ROI/onsets.csv",row.names=FALSE)

correctdata2$logOnset = log(correctdata2$Onset)

modelOn = lmer(logOnset ~ Condition + (Condition|participant) + (1|Verb1)+(1|Verb2), correctdata2, REML=FALSE,control=lmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))) 
summary(modelOn)
Anova(modelOn)
library(lmerTest)
anova(modelOn)
# ts <- fixef(modelOn) / sqrt(diag(vcov(modelOn)))
# print(round(ts,2))
# ps <- 2*(1-pnorm(abs(ts)))
# print(round(ps,3))


#relevel to get difference between SC and SE
correctdata2$Condition <- relevel(correctdata2$Condition, ref = "SC")
modelOn2 = lmer(logOnset ~ Condition + (Condition| participant) + (1|Verb1)+(1|Verb2), correctdata2, REML=FALSE,control=lmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))) 
summary(modelOn2)

ts <- fixef(modelOn2) / sqrt(diag(vcov(modelOn2)))
print(round(ts,2))
ps <- 2*(1-pnorm(abs(ts)))
print(round(ps,3))

```

```{r duration time analysis, echo=TRUE}
correctdata2$logDuration = log(correctdata2$Duration)


modelD = lmer(logDuration ~ Condition + (Condition| participant) + (1|Verb1)+ (1|Verb2), correctdata2, REML=FALSE,control=lmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))) 
summary(modelD)
Anova(modelD)

ts <- fixef(modelD) / sqrt(diag(vcov(modelD)))
print(round(ts,2))
ps <- 2*(1-pnorm(abs(ts)))
print(round(ps,3))
#relevel to get difference between SC and SE
correctdata2$Condition <- relevel(correctdata2$Condition, ref = "SC")
modelD2 = lmer(logDuration ~ Condition + (Condition| participant) + (1|Verb1)+ (1|Verb2), correctdata2, REML=FALSE,control=lmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))) 
summary(modelD2)
ts <- fixef(modelD2) / sqrt(diag(vcov(modelD2)))
print(round(ts,2))
ps <- 2*(1-pnorm(abs(ts)))
print(round(ps,3))

```

## Onsets and duration means for each participant

```{r onsetmeans, echo=FALSE}

#average of correct trials per condition
onsets <- data.frame
onsets <- correctdata %>% group_by(Condition,participant) %>% summarise(onset = mean(Onset))
durations <- data.frame
durations <- correctdata %>% group_by(Condition,participant) %>% summarise(duration = mean(Offset-Onset))



onsets$structure <- ifelse(onsets$Condition == "NP","C1",ifelse(onsets$Condition == "SC","C2",(ifelse(onsets$Condition == "SE","C4","FIL"))))
durations$structure <- ifelse(durations$Condition == "NP","C1",ifelse(durations$Condition == "SC","C2",(ifelse(durations$Condition == "SE","C4","FIL"))))

mean_times = correctdata %>% group_by(Condition) %>% summarise(meanOnset = mean(Onset),sdO=sd(Onset),semO=sd(Onset)/sqrt(40),meanDuration = mean(Offset-Onset),sdD=sd(Offset-Onset),semD=sd(Offset-Onset)/sqrt(40))

mean_times$structure <- ifelse(mean_times$Condition == "NP","C1",ifelse(mean_times$Condition == "SC","C2",(ifelse(mean_times$Condition == "SE","C4","FIL"))))


```
```{r raincloud plot onset condition with means, echo=FALSE}
p7 <- ggplot(onsets,aes(x=structure,y=onset, fill = structure, colour = structure))+
  geom_flat_violin(position = position_nudge(x = .25, y = 0),adjust =2)+
  geom_point(position = position_jitter(width = .15), size = .25)+
  geom_point(data = mean_times, aes(x = structure, y = meanOnset), position = position_nudge(.25), colour = "BLACK")+
  geom_errorbar(data = mean_times, aes(x = structure, y = meanOnset, ymin = meanOnset-semO, ymax = meanOnset+semO), position = position_nudge(.25), colour = "BLACK", width = 0.1, size = 0.8)+
  ylab('Onset (sec)')+xlab('Condition')+theme_mpinl_general()+guides(fill = FALSE, colour = FALSE) +
  #scale_colour_discrete_mpinl()+  scale_fill_discrete_mpinl()+
  scale_colour_grey()+  scale_fill_grey()+

  ggtitle("Production Onset")
p7

p9 <- ggplot(onsets,aes(x=structure,y=onset, fill = structure, colour = structure))+
  geom_flat_violin(position = position_nudge(x = .25, y = 0),adjust =2)+
  geom_point(position = position_jitter(width = .15), size = .8)+
  geom_point(data = mean_times, aes(x = structure, y = meanOnset), position = position_nudge(.25), colour = "BLACK")+
  geom_errorbar(data = mean_times, aes(x = structure, y = meanOnset, ymin = meanOnset-semO, ymax = meanOnset+semO), position = position_nudge(.25), colour = "BLACK", width = 0.1, size = 0.8)+
  ylab('Onset (sec)')+xlab('Condition')+theme_mpinl_poster()+guides(fill = FALSE, colour = FALSE) +
  scale_colour_discrete_mpinl()+
  scale_fill_discrete_mpinl()+
  ggtitle("Production Onset")
p9
```

```{r raincloud plot onset condition with means, echo=FALSE}
p8 <- ggplot(durations,aes(x=structure,y=duration, fill = structure, colour = structure))+
  geom_flat_violin(position = position_nudge(x = .25, y = 0),adjust =2)+
  geom_point(position = position_jitter(width = .15), size = .25)+
  geom_point(data = mean_times, aes(x = structure, y = meanDuration), position = position_nudge(.25), colour = "BLACK")+
  geom_errorbar(data = mean_times, aes(x = structure, y = meanDuration, ymin = meanDuration-semD, ymax = meanDuration+semD), position = position_nudge(.25), colour = "BLACK", width = 0.1, size = 0.8)+
  ylab('Duration (sec)')+xlab('Condition')+theme_mpinl_general()+guides(fill = FALSE, colour = FALSE) +
  #scale_colour_discrete_mpinl()+  scale_fill_discrete_mpinl()+
  scale_color_grey() + scale_fill_grey() +
  ggtitle("Production Duration")
p8
all_plot <- plot_grid(p1, p7, p8, labels="AUTO", nrow=1)
all_plot
ggsave('P:/3011226.01/figures/onset_duration.png', width = 6, height = 3)
ggsave(
  'P:/3011226.01/figures/behav_all_fig.tif',
  plot = last_plot(),
  device = "tiff",
  path = NULL,
  scale = 1,
  width = 180,
  height = 80,
  units = "mm",
  dpi = 300,
  limitsize = TRUE
)


p10 <- ggplot(durations,aes(x=structure,y=duration, fill = structure, colour = structure))+
  geom_flat_violin(position = position_nudge(x = .25, y = 0),adjust =2)+
  geom_point(position = position_jitter(width = .15), size = .8)+
  geom_point(data = mean_times, aes(x = structure, y = meanDuration), position = position_nudge(.25), colour = "BLACK")+
  geom_errorbar(data = mean_times, aes(x = structure, y = meanDuration, ymin = meanDuration-semD, ymax = meanDuration+semD), position = position_nudge(.25), colour = "BLACK", width = 0.1, size = 0.8)+
  ylab('Duration (sec)')+xlab('Condition')+theme_mpinl_poster()+guides(fill = FALSE, colour = FALSE) +
  scale_colour_discrete_mpinl()+
  scale_fill_discrete_mpinl()+
  ggtitle("Production Duration")
p10
all_plot_poster <- plot_grid(p9, p10, labels="AUTO")

#title <- ggdraw() + 
#  draw_label("",
 #            fontface = 'bold')
#
#all_plot_final <- plot_grid(title, all_plot, ncol = 1, rel_heights = c(0.1, 1)) # rel_heights values control title margins


all_plot_poster
ggsave('P:/3011226.01/figures/onset_duration_poster.png', width = 15, height = 7)

```

```{r various plots}

ggplot(onsets, aes(x=Condition, y = onset)) +
  geom_jitter(width=.1,aes(color=participant)) + labs(y= 'Onset' ) + geom_violin(alpha = 0.2)

mean_times = correctdata %>% group_by(Condition) %>% summarise(meanOnset = mean(Onset),sdO=sd(Onset),semO=sd(Onset)/sqrt(40),meanDuration = mean(Offset-Onset),sdD=sd(Offset-Onset),semD=sd(Offset-Onset)/sqrt(40))

```
```{r durationsmeans, echo=FALSE}

#average of correct trials per condition
durations <- data.frame
durations <- correctdata %>% group_by(Condition,participant) %>% summarise(duration = mean(Offset-Onset))

ggplot(durations, aes(x=Condition, y = duration)) +
  geom_jitter(width=.1,aes(color=participant)) + labs(y= 'Duration' ) + geom_violin(alpha = 0.2)

```

## Onsets and duration means for each participant with condition

```{r onsetmeans per cond, echo=FALSE}

#average of correct trials per condition

#accuracy$correct = accuracy$correct/80*100

#mean_accuracy <- accuracy %>% group_by(Condition) %>% summarise(meanC = mean(correct))

ggplot(onsets, aes(x=Condition, y = onset)) +
  geom_col(stat='identity', aes(fill=Condition)) + labs(y= 'Onset' ) +
  coord_cartesian(ylim=c(1,2.3)) +
    facet_grid(.~participant)


```
```{r durationsmeans per cond, echo=FALSE}

#average of correct trials per condition

ggplot(durations, aes(x=Condition, y = duration)) +
  geom_col(stat='identity', aes(fill=Condition)) + labs(y= 'Onset' ) +
  #coord_cartesian(ylim=c(1,3.5)) +
    facet_grid(.~participant)

```


## Raincloud plots per condition

```{r raincloud plot onset condition, echo=FALSE}
p7 <- ggplot(onsets,aes(x=Condition,y=onset))+
  geom_flat_violin(position = position_nudge(x = .25, y = 0),adjust =2, alpha=0.3)+
  geom_point(position = position_jitter(width = .15), size = .25, aes(color = participant))+
  #note that here we need to set the x-variable to a numeric variable and bump it to get the boxplots to line up with the rainclouds.
  #geom_boxplot(aes(x = as.numeric(Condition)+0.25, y = Onset),outlier.shape = NA, alpha = 0.3, width = .1, colour = "BLACK") +
  ylab('Onset')+xlab('Condition')+theme_cowplot() +
  ggtitle("Onset times per condition")

p7
#ggsave('../figs/tutorial_R/5boxplots.png', width = w, height = h)
```
```{r raincloud plot onset condition with means, echo=FALSE}
p7 <- ggplot(onsets,aes(x=Condition,y=onset, fill = Condition, colour = Condition))+
  geom_flat_violin(position = position_nudge(x = .25, y = 0),adjust =2)+
  geom_point(position = position_jitter(width = .15), size = .25)+
  geom_point(data = mean_times, aes(x = Condition, y = meanOnset), position = position_nudge(.25), colour = "BLACK")+
  geom_errorbar(data = mean_times, aes(x = Condition, y = meanOnset, ymin = meanOnset-semO, ymax = meanOnset+semO), position = position_nudge(.25), colour = "BLACK", width = 0.1, size = 0.8)+
  ylab('Onset (sec)')+xlab('Condition')+theme_cowplot()+guides(fill = FALSE, colour = FALSE) +
  scale_colour_brewer(palette = "Dark2")+
  scale_fill_brewer(palette = "Dark2")+
  ggtitle("Production Onset")
p7

```
```{r raincloud plot onset condition with means, echo=FALSE}
p8 <- ggplot(durations,aes(x=Condition,y=duration, fill = Condition, colour = Condition))+
  geom_flat_violin(position = position_nudge(x = .25, y = 0),adjust =2)+
  geom_point(position = position_jitter(width = .15), size = .25)+
  geom_point(data = mean_times, aes(x = Condition, y = meanDuration), position = position_nudge(.25), colour = "BLACK")+
  geom_errorbar(data = mean_times, aes(x = Condition, y = meanDuration, ymin = meanDuration-semD, ymax = meanDuration+semD), position = position_nudge(.25), colour = "BLACK", width = 0.1, size = 0.8)+
  ylab('Duration (sec)')+xlab('Condition')+theme_cowplot()+guides(fill = FALSE, colour = FALSE) +
  scale_colour_brewer(palette = "Dark2")+
  scale_fill_brewer(palette = "Dark2")+
  ggtitle("Production Duration")
p8

all_plot <- plot_grid(p7, p8, labels="AUTO")

#title <- ggdraw() + 
#  draw_label("",
 #            fontface = 'bold')
#
#all_plot_final <- plot_grid(title, all_plot, ncol = 1, rel_heights = c(0.1, 1)) # rel_heights values control title margins


all_plot
ggsave('/project/3011226.01/scripts/onset_duration.png', width = 6, height = 3)
```

```{r raincloud plot durations condition, echo=FALSE}
p8 <- ggplot(durations,aes(x=Condition,y=duration))+
  geom_flat_violin(position = position_nudge(x = .25, y = 0),adjust =2, alpha=0.3)+
  geom_point(position = position_jitter(width = .15), size = .25, aes(color = participant))+
  #note that here we need to set the x-variable to a numeric variable and bump it to get the boxplots to line up with the rainclouds.
  #geom_boxplot(aes(x = as.numeric(Condition)+0.25, y = Onset),outlier.shape = NA, alpha = 0.3, width = .1, colour = "BLACK") +
  ylab('Duration')+xlab('Condition')+theme_cowplot() +
  ggtitle("Durations per condition")

p8
#ggsave('../figs/tutorial_R/5boxplots.png', width = w, height = h)
```

## Raincloud plots per participant

```{r raincloud plot onset, echo=FALSE}
p5 <- ggplot(correctdata,aes(x=participant,y=Onset, fill = Condition))+
  geom_flat_violin(position = position_nudge(x = .25, y = 0),adjust =2, alpha=0.3)+
  geom_point(position = position_jitter(width = .15), size = .25, aes(color = Condition))+
  #note that here we need to set the x-variable to a numeric variable and bump it to get the boxplots to line up with the rainclouds.
  #geom_boxplot(aes(x = as.numeric(Condition)+0.25, y = Onset),outlier.shape = NA, alpha = 0.3, width = .1, colour = "BLACK") +
  ylab('Onset')+xlab('Participant')+theme_cowplot() +
  ggtitle("Onset times per participant")

p5
#ggsave('../figs/tutorial_R/5boxplots.png', width = w, height = h)
```

```{r raincloud plot durations, echo=FALSE}
p6 <- ggplot(correctdata,aes(x=participant,y=Offset-Onset, fill = Condition))+
  geom_flat_violin(position = position_nudge(x = .25, y = 0),adjust =2, alpha=0.3)+
  geom_point(position = position_jitter(width = .15), size = .25, aes(color = Condition))+
  #note that here we need to set the x-variable to a numeric variable and bump it to get the boxplots to line up with the rainclouds.
  #geom_boxplot(aes(x = as.numeric(Condition)+0.25, y = Onset),outlier.shape = NA, alpha = 0.3, width = .1, colour = "BLACK") +
  ylab('Duration')+xlab('Participant')+theme_cowplot() +
  ggtitle("Durations per participant")

p6
#ggsave('../figs/tutorial_R/5boxplots.png', width = w, height = h)
```


#other stuff
```{r raincloud plot, echo=FALSE}
p5 <- ggplot(correctdata,aes(x=participant,y=Onset, fill = Condition))+
  geom_flat_violin(position = position_nudge(x = .25, y = 0),adjust =2)+
  geom_point(position = position_jitter(width = .15), size = .25, aes(color = Condition))+
#note that here we need to set the x-variable to a numeric variable and bump it to get the boxplots to line up with the rainclouds.
#geom_boxplot(aes(x = as.numeric(Condition)+0.25, y = Onset),outlier.shape = NA, alpha = 0.3, width = .1, colour = "BLACK") +
ylab('Onset')+xlab('Condition')+theme_cowplot()+guides(fill = FALSE, colour = FALSE) +
ggtitle("Figure 5: Raincloud Plot w/Boxplots")

p5
#ggsave('../figs/tutorial_R/5boxplots.png', width = w, height = h)
```



```{r onsetoffset, echo=FALSE}
# mean onset and offset across participants


means <- data.frame
means <- correctdata %>% group_by(Condition,participant) %>% summarise(m_onset = mean(Onset), std_onset = sd(Onset), m_duration = mean(Offset - Onset), std_duration = sd(Offset-Onset), m_offset = mean(Offset), std_offset= sd(Offset))
means
p6 <- ggplot(means,aes(x=Condition,y=m_onset, fill = participant))+
geom_flat_violin(position = position_nudge(x = .25, y = 0),adjust =2)+
geom_point(position = position_jitter(width = .15), size = .25)+
#note that here we need to set the x-variable to a numeric variable and bump it to get the boxplots to line up with the rainclouds.
geom_boxplot(aes(x = as.numeric(Condition)+0.25, y = m_onset),outlier.shape = NA, alpha = 0.3, width = .1, colour = "BLACK") +
ylab('Onset')+xlab('Condition')+theme_cowplot()+guides(fill = FALSE, colour = FALSE) +
ggtitle("Figure 5: Raincloud Plot w/Boxplots")
p6


```

```{r participant info, echo=FALSE}
# mean onset and offset across participants


means_p <- data.frame
means <- correctdata %>% group_by(participant,Condition) %>% summarise(m_onset = mean(Onset), std_onset = sd(Onset), m_duration = mean(Offset - Onset), std_duration = sd(Offset-Onset), m_offset = mean(Offset), std_offset= sd(Offset))
means
p7 <- ggplot(means,aes(x=Condition,y=m_onset, fill = participant))+
geom_flat_violin(position = position_nudge(x = .25, y = 0),adjust =2)+
geom_point(position = position_jitter(width = .15), size = .25)+
#note that here we need to set the x-variable to a numeric variable and bump it to get the boxplots to line up with the rainclouds.
geom_boxplot(aes(x = as.numeric(Condition)+0.25, y = m_onset),outlier.shape = NA, alpha = 0.3, width = .1, colour = "BLACK") +
ylab('Onset')+xlab('Condition')+theme_cowplot()+guides(fill = FALSE, colour = FALSE) +
ggtitle("Figure 5: Raincloud Plot w/Boxplots")
p7


```

```{r plot, echo=FALSE}

pl1 = ggplot(correctdata, aes(x=Onset, y=Offset)) + geom_point(aes(color = Condition), alpha=0.5)
pl1
#ggsave('plotill.pdf', device = 'pdf')
ggplot(correctdata, aes(y=Offset-Onset,x=Trial)) + geom_point(aes(color = as.factor(participant)))
plot(correctdata$Offset - correctdata$Onset)


```

Some trials may have been consistently longer across participants.

```{r plottrials, echo=FALSE}

trials <- correctdata %>% group_by(Trial) %>% summarise(m_onset = mean(Onset), SEM_onset = std.error(Onset), m_duration = mean(Offset - Onset), SEM_duration = std.error(Offset - Onset), m_offset = mean(Offset), SEM_offset = std.error(Offset))
trials$condition <- as.factor(c(rep(1,80), rep(2,80), rep(3,80), rep(4,80)))

ggplot(trials, aes(x=m_onset, y=m_duration)) + geom_point(aes(color = condition))

ggplot(trials,aes(x=Trial, y = m_onset)) + geom_point()


```
```{r plottrials, echo=FALSE}

trials$Verb1 = correctdata$Verb1[1:320]
trials$Verb2 = correctdata$Verb2[1:320]

ggplot(trials, aes(x=Trial, y=m_duration)) + geom_point(aes(color = Verb2))

ggplot(trials,aes(x=Trial, y = m_onset)) + geom_point(aes(color = Verb1))

ggplot(trials, aes(x=Verb1, y = m_onset)) + geom_point(aes(color=Verb1))

```

```{r plotverbs, echo=FALSE}

verb1 <- correctdata %>% group_by(Verb1) %>% summarise(m_onset = mean(Onset), SEM_onset = std.error(Onset), m_duration = mean(Offset - Onset), SEM_duration = std.error(Offset - Onset), m_offset = mean(Offset), SEM_offset = std.error(Offset))

ggplot(verb1[0:20,], aes(x=m_onset, y=m_duration)) + geom_violin(aes(color = Verb1))

ggplot(trials,aes(x=Trial, y = m_onset)) + geom_point()


```
```{r plotverbs, echo=FALSE}

verb1 <- correctdata %>% group_by(Verb1) %>% summarise(m_onset = mean(Onset), std_onset = sd(Onset), SEM_onset = std.error(Onset), m_duration = mean(Offset - Onset), std_duration = sd(Offset-Onset), SEM_duration = std.error(Offset - Onset), m_offset = mean(Offset), std_offset = sd(Offset), SEM_offset = std.error(Offset))


ggplot(verb1, aes(x=Verb1, y=m_offset)) + geom_point(aes(color = Verb1))

ggplot(verb1, aes(x=Verb1, y=m_onset)) + geom_point(aes(color = Verb1))

ggplot(verb1, aes(x=Verb1, y=m_duration)) + geom_point(aes(color = Verb1))

ggplot(trials,aes(x=Trial, y = m_onset)) + geom_point()


```