---
title: "Onset and duration analysis of sentence production fMRI experiment"
author: "Laura Giglio"
date: "2019 09 24"
output:
  word_document: default
  pdf_document: default
  html_document: default
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = 'P:/3011226.01/behavioural/')
library(ggplot2)
library(plyr)
library(dplyr)
library(tidyverse)
library(plotrix)
library(reshape2)
rm(list=ls())
#setwd("P:/3011226.01/behavioural/")
packages <- c("ggplot2", "dplyr", "lavaan", "plyr", "cowplot", "rmarkdown", 
              "readr", "caTools", "bitops")
if (length(setdiff(packages, rownames(installed.packages()))) > 0) {
  install.packages(setdiff(packages, rownames(installed.packages())))  
}
library(cowplot)
library(dplyr)
library(readr)

source("C:/Users/laugig/Documents/RainCloudPlots-master/RainCloudPlots-master/tutorial_R/R_rainclouds.R")
#source("summarySE.R")
#source("simulateData.R")
```
Importing coding data and Importing onset and offset marking

```{r import, echo=FALSE, warning=FALSE}

#import coding results
#setwd("P:/3011226.01/behavioural/")
coded_subjs = c("01","02","03","04","06","07","08","09","10","11","12","13","14","15","16","17","18","19","20","21","22","24","25", "26","27","28", "29","30","31","32","33","34","35","36","37","38","39","40","41","42","43","44","46")
accdata = data.frame()
praatdata = data.frame()
for (isubj in coded_subjs) {
  
  #open file
  dirpath = paste("P:/3011226.01/behavioural/s", isubj, sep="")
  allfilenames = dir(dirpath, pattern = "P._run*")
  for (irun in 1:length(allfilenames)) {
    
    # get run order
    run_order = read.table(paste("s", isubj, "/s", isubj, ".txt", sep="" ), header = T, sep = '\t')
    
    # get accuracy files
    filename = paste("P:/3011226.01/behavioural/s", isubj, "/", allfilenames[run_order$Order_runs[irun]], sep="")
    temp = read.delim(filename, header = T, sep = '\t')
    temp$Actor <- NULL
    temp$X <- NULL
    # add subj and run numer
    #subjnr = unlist(strsplit(filename, "_"))[2]
    temp$participant = as.factor(isubj)
    temp$run = as.factor(irun)
  
    #combine with other files
    accdata = rbind(accdata,temp)

    # get onset offset times from praat txt file
    filename2 = paste("P:/3011226.01/behavioural/s", isubj, "/", irun, "/filtered/onsets_durationAutomatic.txt", sep="")
    temp2 = read.table(filename2, header = F, sep = '\t')
    
    # add subj and run number
    temp2$participant = as.factor(isubj)
    
    temp2$run = as.factor(irun)
    #combine with other files
    praatdata = rbind(praatdata,temp2)
  }
}
```

Merging accuracy and praat data

```{r mergedata, echo=FALSE}
# first need to sort praat data in "normal" order
praatdata$V2 <- as.character(praatdata$V2)
for (n in 1:nrow(praatdata)) {
  praatdata$trialnr[n] = unlist(strsplit(praatdata$V2[n], "_"))[3]
}
praatdata = subset(praatdata, select= -V5)
praatdata = subset(praatdata, select= -V1)
colnames(praatdata)[1] = 'Recording'
colnames(praatdata)[2] = 'Onset'
colnames(praatdata)[3] = 'Offset'

praatdata <- praatdata[order(as.integer(praatdata$participant), as.integer(praatdata$run), as.integer(praatdata$trialnr)),]

alldata = cbind(praatdata,accdata)
alldata = subset(alldata, select= -participant)
alldata = subset(alldata, select= -run.1)
 
```
## Accuracy

Legend:

FIL = fillers, "De man raakt de vrouw" (the man touches the woman)

NP = noun phrase, "denken, springen, de man, de vrouw" (to think, to jump, the man, the woman)

SC = coordinated sentence, "de man rent, de vrouw springt" (the man runs, the woman jumps)

SE = embedded sencence, "de man denkt dat de vrouw springt" (the man thinks that the woman jumps)



Correct number of trials per participant

```{r correct, echo=FALSE}
#alldata$Coding[875] = 1
alldata$Accuracy2 = ifelse(alldata$Accuracy2 == 1, 1,2)

#as.data.frame.matrix(table(alldata$Accuracy2,alldata$participant,alldata$Condition))
#table(alldata$Accuracy,alldata$participant,alldata$Condition)
#a = as.data.frame.matrix(table(alldata$Accuracy2,alldata$Condition)/10)
#ab = melt(a)
#ggplot(ab,aes(x=variable, y = value)) + geom_bar(stat= 'identity')
#a
#
#average of correct trials per condition
accuracy <- data.frame
accuracy <- alldata %>% group_by(Condition,participant) %>% summarise(correct = sum(Accuracy2==1))

accuracy$correct = accuracy$correct/80*100 #to get percentage

mean_accuracy <- accuracy %>% group_by(Condition) %>% summarise(meanC = mean(correct))
mean_participant <- accuracy %>% group_by(participant) %>% summarise(meanC = mean(correct))
#mean_participant2 <- alldata %>% group_by(participant) %>% summarise(correct = sum(Accuracy2==1)/320*100)

m = mean(mean_participant$meanC)
sdp = sd(mean_participant$meanC)
# mean accuracy per participant
ggplot(mean_participant, aes(x=participant, y=meanC, fill = meanC)) + geom_bar(stat='identity')

#mean accuracy per condition
ggplot(accuracy, aes(x=Condition, y=correct)) + geom_bar(stat='identity')

#ggplot(accuracy, aes(x=correct)) + geom_bar()


```
```{r accuracyplot, echo=FALSE}
accuracyplot = ggplot(accuracy, aes(x=Condition, y = correct)) +
  geom_jitter(width=.1,aes(color=participant)) + labs(y= '% Correct responses' ) +
  geom_violin(alpha=0.3)

#ggsave('accuracy_plot.pdf', plot=accuracyplot)

accuracyplot
```

```{r makecorrect, echo=FALSE}
#only keep correct trials
correctdata = droplevels(alldata[alldata$Accuracy2=='1',])


#there's an extra NA row, delete for now
#correctdata = correctdata[-851,]

#correctdata = read.csv('correctdata.csv')
#correctdata = write.csv(correctdata, 'correctdata.csv', row.names = FALSE)
```

## Onsets and duration means for each participant

```{r onsetmeans, echo=FALSE}

#average of correct trials per condition
onsets <- data.frame
onsets <- correctdata %>% group_by(Condition,participant) %>% summarise(onset = mean(Onset))

#accuracy$correct = accuracy$correct/80*100

#mean_accuracy <- accuracy %>% group_by(Condition) %>% summarise(meanC = mean(correct))

ggplot(onsets, aes(x=Condition, y = onset)) +
  geom_jitter(width=.1,aes(color=participant)) + labs(y= 'Onset' ) + geom_violin(alpha = 0.2)

```
```{r durationsmeans, echo=FALSE}

#average of correct trials per condition
durations <- data.frame
durations <- correctdata %>% group_by(Condition,participant) %>% summarise(duration = mean(Offset-Onset))

ggplot(durations, aes(x=Condition, y = duration)) +
  geom_jitter(width=.1,aes(color=participant)) + labs(y= 'Duration' ) + geom_violin(alpha = 0.2)

```

<!-- ## Onsets and duration means for each participant with condition -->

<!-- ```{r onsetmeans per cond, echo=FALSE} -->

<!-- #average of correct trials per condition -->

<!-- #accuracy$correct = accuracy$correct/80*100 -->

<!-- #mean_accuracy <- accuracy %>% group_by(Condition) %>% summarise(meanC = mean(correct)) -->

<!-- ggplot(onsets, aes(x=Condition, y = onset)) + -->
<!--   geom_col(stat='identity', aes(fill=Condition)) + labs(y= 'Onset' ) + -->
<!--   coord_cartesian(ylim=c(1,2.3)) + -->
<!--     facet_grid(.~participant) -->


<!-- ``` -->
<!-- ```{r durationsmeans per cond, echo=FALSE} -->

<!-- #average of correct trials per condition -->

<!-- ggplot(durations, aes(x=Condition, y = duration)) + -->
<!--   geom_col(stat='identity', aes(fill=Condition)) + labs(y= 'Onset' ) + -->
<!--   #coord_cartesian(ylim=c(1,3.5)) + -->
<!--     facet_grid(.~participant) -->

<!-- ``` -->


<!-- ## Raincloud plots per condition -->

<!-- ```{r raincloud plot onset condition, echo=FALSE} -->
<!-- p7 <- ggplot(onsets,aes(x=Condition,y=onset))+ -->
<!--   geom_flat_violin(position = position_nudge(x = .25, y = 0),adjust =2, alpha=0.3)+ -->
<!--   geom_point(position = position_jitter(width = .15), size = .25, aes(color = participant))+ -->
<!--   #note that here we need to set the x-variable to a numeric variable and bump it to get the boxplots to line up with the rainclouds.  -->
<!--   #geom_boxplot(aes(x = as.numeric(Condition)+0.25, y = Onset),outlier.shape = NA, alpha = 0.3, width = .1, colour = "BLACK") + -->
<!--   ylab('Onset')+xlab('Condition')+theme_cowplot() + -->
<!--   ggtitle("Onset times per condition") -->

<!-- p7 -->
<!-- #ggsave('../figs/tutorial_R/5boxplots.png', width = w, height = h) -->
<!-- ``` -->

<!-- ```{r raincloud plot durations condition, echo=FALSE} -->
<!-- p8 <- ggplot(durations,aes(x=Condition,y=duration))+ -->
<!--   geom_flat_violin(position = position_nudge(x = .25, y = 0),adjust =2, alpha=0.3)+ -->
<!--   geom_point(position = position_jitter(width = .15), size = .25, aes(color = participant))+ -->
<!--   #note that here we need to set the x-variable to a numeric variable and bump it to get the boxplots to line up with the rainclouds.  -->
<!--   #geom_boxplot(aes(x = as.numeric(Condition)+0.25, y = Onset),outlier.shape = NA, alpha = 0.3, width = .1, colour = "BLACK") + -->
<!--   ylab('Duration')+xlab('Condition')+theme_cowplot() + -->
<!--   ggtitle("Durations per condition") -->

<!-- p8 -->
<!-- #ggsave('../figs/tutorial_R/5boxplots.png', width = w, height = h) -->
<!-- ``` -->

<!-- ## Raincloud plots per participant -->

<!-- ```{r raincloud plot onset, echo=FALSE} -->
<!-- p5 <- ggplot(correctdata,aes(x=participant,y=Onset, fill = Condition))+ -->
<!--   geom_flat_violin(position = position_nudge(x = .25, y = 0),adjust =2, alpha=0.3)+ -->
<!--   geom_point(position = position_jitter(width = .15), size = .25, aes(color = Condition))+ -->
<!--   #note that here we need to set the x-variable to a numeric variable and bump it to get the boxplots to line up with the rainclouds.  -->
<!--   #geom_boxplot(aes(x = as.numeric(Condition)+0.25, y = Onset),outlier.shape = NA, alpha = 0.3, width = .1, colour = "BLACK") + -->
<!--   ylab('Onset')+xlab('Participant')+theme_cowplot() + -->
<!--   ggtitle("Onset times per participant") -->

<!-- p5 -->
<!-- #ggsave('../figs/tutorial_R/5boxplots.png', width = w, height = h) -->
<!-- ``` -->

<!-- ```{r raincloud plot durations, echo=FALSE} -->
<!-- p6 <- ggplot(correctdata,aes(x=participant,y=Offset-Onset, fill = Condition))+ -->
<!--   geom_flat_violin(position = position_nudge(x = .25, y = 0),adjust =2, alpha=0.3)+ -->
<!--   geom_point(position = position_jitter(width = .15), size = .25, aes(color = Condition))+ -->
<!--   #note that here we need to set the x-variable to a numeric variable and bump it to get the boxplots to line up with the rainclouds.  -->
<!--   #geom_boxplot(aes(x = as.numeric(Condition)+0.25, y = Onset),outlier.shape = NA, alpha = 0.3, width = .1, colour = "BLACK") + -->
<!--   ylab('Duration')+xlab('Participant')+theme_cowplot() + -->
<!--   ggtitle("Durations per participant") -->

<!-- p6 -->
<!-- #ggsave('../figs/tutorial_R/5boxplots.png', width = w, height = h) -->
<!-- ``` -->


<!-- #other stuff -->
<!-- ```{r raincloud plot, echo=FALSE} -->
<!-- p5 <- ggplot(correctdata,aes(x=participant,y=Onset, fill = Condition))+ -->
<!--   geom_flat_violin(position = position_nudge(x = .25, y = 0),adjust =2)+ -->
<!--   geom_point(position = position_jitter(width = .15), size = .25, aes(color = Condition))+ -->
<!-- #note that here we need to set the x-variable to a numeric variable and bump it to get the boxplots to line up with the rainclouds. -->
<!-- #geom_boxplot(aes(x = as.numeric(Condition)+0.25, y = Onset),outlier.shape = NA, alpha = 0.3, width = .1, colour = "BLACK") + -->
<!-- ylab('Onset')+xlab('Condition')+theme_cowplot()+guides(fill = FALSE, colour = FALSE) + -->
<!-- ggtitle("Figure 5: Raincloud Plot w/Boxplots") -->

<!-- p5 -->
<!-- #ggsave('../figs/tutorial_R/5boxplots.png', width = w, height = h) -->
<!-- ``` -->



<!-- ```{r onsetoffset, echo=FALSE} -->
<!-- # mean onset and offset across participants -->


<!-- means <- data.frame -->
<!-- means <- correctdata %>% group_by(Condition,participant) %>% summarise(m_onset = mean(Onset), std_onset = sd(Onset), m_duration = mean(Offset - Onset), std_duration = sd(Offset-Onset), m_offset = mean(Offset), std_offset= sd(Offset)) -->
<!-- means -->
<!-- p6 <- ggplot(means,aes(x=Condition,y=m_onset, fill = participant))+ -->
<!-- geom_flat_violin(position = position_nudge(x = .25, y = 0),adjust =2)+ -->
<!-- geom_point(position = position_jitter(width = .15), size = .25)+ -->
<!-- #note that here we need to set the x-variable to a numeric variable and bump it to get the boxplots to line up with the rainclouds. -->
<!-- geom_boxplot(aes(x = as.numeric(Condition)+0.25, y = m_onset),outlier.shape = NA, alpha = 0.3, width = .1, colour = "BLACK") + -->
<!-- ylab('Onset')+xlab('Condition')+theme_cowplot()+guides(fill = FALSE, colour = FALSE) + -->
<!-- ggtitle("Figure 5: Raincloud Plot w/Boxplots") -->
<!-- p6 -->


<!-- ``` -->

<!-- ```{r participant info, echo=FALSE} -->
<!-- # mean onset and offset across participants -->


<!-- means_p <- data.frame -->
<!-- means <- correctdata %>% group_by(participant,Condition) %>% summarise(m_onset = mean(Onset), std_onset = sd(Onset), m_duration = mean(Offset - Onset), std_duration = sd(Offset-Onset), m_offset = mean(Offset), std_offset= sd(Offset)) -->
<!-- means -->
<!-- p7 <- ggplot(means,aes(x=Condition,y=m_onset, fill = participant))+ -->
<!-- geom_flat_violin(position = position_nudge(x = .25, y = 0),adjust =2)+ -->
<!-- geom_point(position = position_jitter(width = .15), size = .25)+ -->
<!-- #note that here we need to set the x-variable to a numeric variable and bump it to get the boxplots to line up with the rainclouds. -->
<!-- geom_boxplot(aes(x = as.numeric(Condition)+0.25, y = m_onset),outlier.shape = NA, alpha = 0.3, width = .1, colour = "BLACK") + -->
<!-- ylab('Onset')+xlab('Condition')+theme_cowplot()+guides(fill = FALSE, colour = FALSE) + -->
<!-- ggtitle("Figure 5: Raincloud Plot w/Boxplots") -->
<!-- p7 -->


<!-- ``` -->

<!-- ```{r plot, echo=FALSE} -->

<!-- pl1 = ggplot(correctdata, aes(x=Onset, y=Offset)) + geom_point(aes(color = Condition), alpha=0.5) -->
<!-- pl1 -->
<!-- #ggsave('plotill.pdf', device = 'pdf') -->
<!-- ggplot(correctdata, aes(y=Offset-Onset,x=Trial)) + geom_point(aes(color = as.factor(participant))) -->
<!-- plot(correctdata$Offset - correctdata$Onset) -->


<!-- ``` -->

<!-- Some trials may have been consistently longer across participants. -->

<!-- ```{r plottrials, echo=FALSE} -->

<!-- trials <- correctdata %>% group_by(Trial) %>% summarise(m_onset = mean(Onset), SEM_onset = std.error(Onset), m_duration = mean(Offset - Onset), SEM_duration = std.error(Offset - Onset), m_offset = mean(Offset), SEM_offset = std.error(Offset)) -->
<!-- trials$condition <- as.factor(c(rep(1,80), rep(2,80), rep(3,80), rep(4,80))) -->

<!-- ggplot(trials, aes(x=m_onset, y=m_duration)) + geom_point(aes(color = condition)) -->

<!-- ggplot(trials,aes(x=Trial, y = m_onset)) + geom_point() -->


<!-- ``` -->
<!-- ```{r plottrials, echo=FALSE} -->

<!-- trials$Verb1 = correctdata$Verb1[1:320] -->
<!-- trials$Verb2 = correctdata$Verb2[1:320] -->

<!-- ggplot(trials, aes(x=Trial, y=m_duration)) + geom_point(aes(color = Verb2)) -->

<!-- ggplot(trials,aes(x=Trial, y = m_onset)) + geom_point(aes(color = Verb1)) -->

<!-- ggplot(trials, aes(x=Verb1, y = m_onset)) + geom_point(aes(color=Verb1)) -->

<!-- ``` -->

<!-- ```{r plotverbs, echo=FALSE} -->

<!-- verb1 <- correctdata %>% group_by(Verb1) %>% summarise(m_onset = mean(Onset), SEM_onset = std.error(Onset), m_duration = mean(Offset - Onset), SEM_duration = std.error(Offset - Onset), m_offset = mean(Offset), SEM_offset = std.error(Offset)) -->

<!-- ggplot(verb1[0:20,], aes(x=m_onset, y=m_duration)) + geom_violin(aes(color = Verb1)) -->

<!-- ggplot(trials,aes(x=Trial, y = m_onset)) + geom_point() -->


<!-- ``` -->
<!-- ```{r plotverbs, echo=FALSE} -->

<!-- verb1 <- correctdata %>% group_by(Verb1) %>% summarise(m_onset = mean(Onset), std_onset = sd(Onset), SEM_onset = std.error(Onset), m_duration = mean(Offset - Onset), std_duration = sd(Offset-Onset), SEM_duration = std.error(Offset - Onset), m_offset = mean(Offset), std_offset = sd(Offset), SEM_offset = std.error(Offset)) -->


<!-- ggplot(verb1, aes(x=Verb1, y=m_offset)) + geom_point(aes(color = Verb1)) -->

<!-- ggplot(verb1, aes(x=Verb1, y=m_onset)) + geom_point(aes(color = Verb1)) -->

<!-- ggplot(verb1, aes(x=Verb1, y=m_duration)) + geom_point(aes(color = Verb1)) -->

<!-- ggplot(trials,aes(x=Trial, y = m_onset)) + geom_point() -->


<!-- ``` -->